\huge{A Strategy-Proof Budget Feasible Online Mechanism for Crowdsensing with Time-Discounting Values}

### 2016-11-15 paper.tex
bib

Mobile crowdsensing is a novel application paradigm that utilizes mobile devices to collect, analyze, and share their local information~\cite{ganti2011mobile,lane2010survey}. It usually consists of a service provider, service requesters, and mobile device users. The service provider (a.k.a., the crowdsensing platform), which usually resides in the cloud, recruits participants from mobile device users to upload their sensing data, and then provides services to service requesters based on the collected information. A wide variety of applications has emerged in recent years, including NoiseTube~\cite{maisonneuve2009noisetube} and Ear-phone~\cite{rana2010ear} for noise monitoring, SignalGuru~\cite{koukoumidis2011signalguru} and CrowdAtlas~\cite{wang2013crowdatlas} for traffic monitoring, and CrowdPark~\cite{yan2011crowdpark}, Parknet~\cite{mathur2010parknet} for finding on-street parking spots.

>>>>

Mobile crowdsensing is a novel application paradigm that utilizes mobile devices to collect, analyze, and share their local information~\cite{ganti2011mobile,lane2010survey,Tuncay:2013:PRD:2500423.2504573,6069707,6341381}. It usually consists of a service provider, service requesters, and mobile device users. The service provider (a.k.a., the crowdsensing platform), which usually resides in the cloud, recruits participants from mobile device users to upload their sensing data, and then provides services to service requesters based on the collected information. A wide variety of applications has emerged in recent years, including NoiseTube~\cite{maisonneuve2009noisetube} and Ear-phone~\cite{rana2010ear} for noise monitoring, SignalGuru~\cite{koukoumidis2011signalguru} and CrowdAtlas~\cite{wang2013crowdatlas} for traffic monitoring, and CrowdPark~\cite{yan2011crowdpark}, Parknet~\cite{mathur2010parknet} for finding on-street parking spots.
